Rank Comparison

### 2024-06-20 Code/RankComparison.Rmd
blinded supplemental files, removed noprelim data from readme
added womens 2022 vs 2023 data

---
title: "Rank Comparison"
author: "Owen Fiore"
date: "2023-11-03"
output: pdf_document
---

@@

>>>>

---
title: "Rank Comparison"
author: "Blinded"
date: "2023-12-01"
output: pdf_document
---

@@

Now we test the womens 2022 vs 2023
```{r}
womens <- read.csv("../Data/Clusrank2022vs2023Womens.csv")
colnames(womens) <- c("Time", "Athlete", "Year")
```

The tests below are very similar to the ones above, the only difference being
grouping by Year (0 if 2022 and 1 if 2023).
```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = womens,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = womens,
                method = "ds",
                exact = TRUE, B = 500000)
```
